\documentclass{book}
\usepackage{array}
\usepackage{tcolorbox}
\usepackage{tabularx}
\usepackage{multicol}
\usepackage{geometry}
\usepackage{stix}
\usepackage{makecell}
\usepackage{lib/location}
\usepackage{lib/npc}
\geometry{margin=.75 in}
\begin{document}
	\begin{locationbox}{holden's office}
		\begin{multicols}{2}
		Deputy Chief David Holden directs his Blade Runners from his
		smoke-filled office in the LAPD headquarters. The briefing for
		the player characters is held here, and they can come back here
		to consult with Holden during the course of the investigation.
		You an read more about Holden and the LAPD HQ on page 157 of the
		BLADE RUNNER RPG Core Rulebook.
		\begin{description}
			\item[\color{titlered}\textsf{NPCS:}]Just the Deputy Chief himself.
			\item[\color{titlered}\textsf{CLUES:}] Holden can point the
				player characters in the right direction if they
				need guidance on where to go next. Exactly what
				advice he offers depends on the situation. Be
				careful not to give away too much - the players
				should still do most of the thinking. Examples:
				\begin{itemize}
					\item[\color{titlered}{$\blackinwhitesquare$}]
						{\color{titlered}ESPER WALL.}
						Check the Esper Wall for any images of Leah leaving
						the Snake Pit. And if you do,
						don't forget to use the image
						enhancer to search the images
						for clues.
					\item[\color{titlered}{$\blackinwhitesquare$}]
						{\color{titlered}LEAH'S
						PERSONNEL FILE. }
						Leah had some performance issues
						and failed a Baseline Test a
						while back. It might be a good
						idea to check her personnel
						files in the LAPD Mainframe, and
						her apartment.
					\item[\color{titlered}{$\blackinwhitesquare$}]
						{\color{titlered}ANMOID ROW.
						}
						Vendors sell artificial animals
						(after the player characters
						have found the butterfly jar in 
						Leah's apartment).
					\item[\color{titlered}{$\blackinwhitesquare$}]
						{\color{titlered} BULLET
						BOB's. }
						There is a vendor in Hawker's
						Circle in Sector 4 called Bullet
						Bob's Runner Surplus who sells
						surplus Blade Runner Gear (after
						the player characters
						have learned that Sandor
						was killed by a Blade
						Runner blaster).
					\item[\color{titlered}{$\blackinwhitesquare$}]
						{\color{titlered} THE
						AURELIAN. }
						Stake out the Aurelian - he
						might know more than he is
						telling (after the player
							characters have visited
						the Aurelian).
					\item[\color{titlered}{$\blackinwhitesquare$}]
						{\color{titlered} THE
						HOLLYWOOD SIGN. }
						The ``sign in the Kipple'' - it
						can only mean the old Hollywood
						Sign in the Hollywood Hills
						(after the player characters
							have overheard Styles
							and the Aurelian talking
						in the Safehouse).
				\end{itemize}
			\item[\textsf{\color{titlered}FALLOUT:}]
				Going back to Holden for advice during the
				investiation will cost the player characters a
				precious Shift of time and a Promotion Point
				each, as holden doesn't enjoy hand-holding his
				Blade Runners.
		\end{description}
	\end{multicols}
	\end{locationbox}
	
	\begin{npc}{JELLE SCHYLAR}
		\begin{multicols}{2}
		The infamous publisher of KILL magazine is a genius at shamelessly manipulating ignorant masses and stirring controversy for profit. He is arrogant, aggressive, and boisterous.
		\end{multicols}
		\begin{tcolorbox}[
				notitle,
				sidebyside,
				colframe=\colback,
				sharp corners=all
			]
		\newcolumntype{S}{>
		{\setlength\hsize{2 in}\raggedleft}X}%
		\begin{tabularx}{3 in}{l S}
			Aattributes & 
				Strength B\\
				Agility D\\
				Intelligence B\\
				Empathy A\tabularnewline
			\hline
			Health & 4 \tabularnewline
			\hline
			Resolve & 6 \tabularnewline
			\hline
			Skills &
				Firearms C\\
				Manipulation A\\
				Insight B\tabularnewline
			\hline
			Specialities & - \tabularnewline
			\hline
			Gear & A shotgun under the desk.\tabularnewline
		\end{tabularx}
		\tcblower
		\end{tcolorbox}
	\end{npc}
\end{document}
